\sysfull

### 2019-06-25 paper/TOSN/response-letter/responseLetter.tex

\response{These typos are corrected.}

\end{responses}

\begin{additionalQuestions}
\referee{Does this paper cite and use appropriate references?: No\\
If not, what important references are missing?: 
Ratchet and Clank were the first to propose using a timer for breaking up a long task so that it can make forward progress during short power cycles.  The authors propose the idea as if they were the first to use it.}

\response{Ratchet and Clank are mentioned and referenced in our original paper. 
In Section 4.2, we explicitly mentioned that the timer-based approach is similar to [72]; [72] references the ``Ratchet'' paper. 
In section 9 we explained the core difference between our timer-based approach and the approach explained  in ``Ratchet'' paper. Furthermore, In section 9 and in Table 1 we mentioned Ratchet and Clank by names.}
\end{additionalQuestions}

### 2019-06-25 paper/TOSN/relatedwork.tex
related work and minor revision

\paragraph{Checkpointing-based Systems.}
Early work on energy-harvesting runtimes, such as Dewdrop~\cite{dewdrop}, assumed simple computations that complete on a predictable burst of energy.
%
%Eon~\cite{sorber_sensys_2007} has scheduled such computation based on priority.
%
Support for computation that spans power failures was first achieved with statically-placed conditional checkpoints in Mementos~\cite{mementos}. 
%Mementos left the possibility of non-volatile state becoming inconsistent with volatile state saved in the checkpoint, rendering in-place writes to data structures in non-volatile memory unsafe~\cite{mspcdino}. 
DINO~\cite{dino} addressed the consistency problem by selectively versioning non-volatile state within the checkpoints. Ratchet~\cite{ratchet} ensured consistency by placing a checkpoint at the beginning of each idempotent region in the code. Ratchet has a similar technique to task splitting with a core difference: the checkpoint is of a fixed size, while \sys privatizes a varying number of memory pages.
%
%Ratchet has a similar technique to task splitting with some essential differences: (i) It does not need to handle non-volatile memory accesses, since it assumes a unified non-volatile memory, whereas \sys has to save the volatile pages in non-volatile memory; (ii) The checkpoint is of a fixed size, while \sys privatize variant number of memory pages. 
%
Clank~\cite{hicks_isca_2017} ensured consistency with custom hardware that dynamically tracks WAR dependencies in memory accesses and checkpoints on demand. The consistency problem was also approached with a combination of undo- and redo-logging in software~\cite{baghsorkhi_cgo_2018}. Just-in-time checkpointing, such as Quickrecall~\cite{quickrecall} and Hibernus++~\cite{hibernusplusplus}, eschews inconsistency by saving all volatile state immediately before power failure and halting the execution. Unlike \sys, such systems rely on introspection hardware to monitor supply voltage and on accurate worst-case bounds on checkpoint cost.

In all of the above systems, with the exception of DINO~\cite{dino}, checkpoints are dynamic, i.e., the programmer does not have explicit control over the point at which the code may be resumed after power failure. Dynamic checkpointing systems make it difficult for the programmer to respect application-level atomicity constraints, such as correlating sensor readings. Checkpointing systems that copy most volatile state scale poorly as the size of volatile memory increases.  QuickRecall, Clank and Ratchet reduce the copying overhead by allocating the stack in non-volatile memory---requires more time and energy to access than volatile memory (cf. Section~\ref{sec:cost_task-based}) and not a viable option for off-chip non-volatile memory. In addition, QuickRecall and Clank require custom hardware.

\paragraph{Task-based Systems.}
Alternatives to checkpointing are recent systems based on static tasks, such as Chain~\cite{chain}, Alpaca~\cite{alpaca} and Mayfly~\cite{hester_sensys_2017}. Using static tasks, they eliminate the need to checkpoint volatile state. Using channel-based memory models~\cite{chain,hester_sensys_2017} or automatic privatization and redo-logging~\cite{alpaca} they avoid checkpointing overheads. Moreover, task-based models facilitate respecting application-level atomicity constraints. \sys also relies on
statically defined tasks to avoid checkpointing volatile state. However, unlike prior systems, \sys coalesces its statically-defined tasks at runtime into more efficient dynamic tasks that adapt to changing energy conditions. \sys's mechanism for ensuring memory consistency also differs from the channel-based~\cite{chain} and privatization-based~\cite{alpaca} mechanisms in prior systems. \sys keeps memory consistent through memory virtualization optimized for bulk accesses to task-shared data with high locality.

>>>>

\paragraph{Checkpointing-based Systems.}
Early work on energy-harvesting runtimes, such as Dewdrop~\cite{dewdrop}, assumed simple computations that complete on a predictable burst of energy.
%
%Eon~\cite{sorber_sensys_2007} has scheduled such computation based on priority.
%
Support for computation that spans power failures was first achieved with statically-placed conditional checkpoints in Mementos~\cite{mementos}. 
%Mementos left the possibility of non-volatile state becoming inconsistent with volatile state saved in the checkpoint, rendering in-place writes to data structures in non-volatile memory unsafe~\cite{mspcdino}. 
DINO~\cite{dino} addressed the consistency problem by selectively versioning non-volatile state within the checkpoints. Ratchet~\cite{ratchet} ensured consistency by placing a checkpoint at the beginning of each idempotent region in the code. Ratchet has a similar technique to task splitting with a core difference: the checkpoint is of a fixed size, while \sys privatizes a varying number of memory pages.
%
%Ratchet has a similar technique to task splitting with some essential differences: (i) It does not need to handle non-volatile memory accesses, since it assumes a unified non-volatile memory, whereas \sys has to save the volatile pages in non-volatile memory; (ii) The checkpoint is of a fixed size, while \sys privatize variant number of memory pages. 
%
Clank~\cite{hicks_isca_2017} ensured consistency with custom hardware that dynamically tracks WAR dependencies in memory accesses and checkpoints on demand. The consistency problem was also approached with a combination of undo- and redo-logging in software~\cite{baghsorkhi_cgo_2018}. Just-in-time checkpointing, such as Quickrecall~\cite{quickrecall} and Hibernus++~\cite{hibernusplusplus}, eschews inconsistency by saving all volatile state immediately before a power failure and halting the execution. Unlike \sys, such systems rely on introspection hardware to monitor supply voltage and on accurate worst-case bounds on checkpoint cost.

In all of the above systems, with the exception of DINO~\cite{dino}, checkpoints are dynamic, i.e., the programmer does not have explicit control over the point at which the code may be resumed after power failure. Dynamic checkpointing systems make it difficult for the programmer to respect application-level atomicity constraints, such as correlating sensor readings. Checkpointing systems that copy most volatile state scale poorly as the size of volatile memory increases.  QuickRecall, Clank, and Ratchet reduce the copying overhead by allocating the stack in non-volatile memory---requires more time and energy to access than volatile memory (cf. Section~\ref{sec:cost_task-based}) and not a viable option for off-chip non-volatile memory. In addition, QuickRecall and Clank require custom hardware.

\paragraph{Task-based Systems.}
Alternatives to checkpointing are recent systems based on static tasks, such as Chain~\cite{chain}, Alpaca~\cite{alpaca}, inK~\cite{yildirim2018ink}, and Mayfly~\cite{hester_sensys_2017}. Using static tasks, they eliminate the need to checkpoint volatile state. Using channel-based memory models~\cite{chain,hester_sensys_2017} or automatic privatization and redo-logging~\cite{alpaca} they avoid checkpointing overheads. Moreover, task-based models facilitate respecting application-level atomicity constraints. \sys also relies on
statically defined tasks to avoid checkpointing volatile state. However, unlike prior systems, \sys coalesces its statically-defined tasks at runtime into more efficient dynamic tasks that adapt to changing energy conditions. \sys's mechanism for ensuring memory consistency also differs from the channel-based~\cite{chain} and privatization-based~\cite{alpaca} mechanisms in prior systems. \sys keeps memory consistent through memory virtualization optimized for bulk accesses to task-shared data with high locality.
